\documentclass[11pt]{article}
\usepackage{pgf}
\usepackage{listings}

% the following produces 1 inch margins all around with no header or footer
\topmargin  =10.mm    % beyond 25.mm
\oddsidemargin  =0.mm   % beyond 25.mm
\evensidemargin =0.mm   % beyond 25.mm
\headheight =0.mm
\headsep  =0.mm
\textheight =220.mm
\textwidth  =165.mm

\lstset{basicstyle=\footnotesize,columns=fullflexible,frame=lines,numbers=left,numberstyle=\tiny,stepnumber=5}


\lstdefinelanguage{CSharp}
{
 morecomment = [l]{//}, 
 morecomment = [l]{///},
 morecomment = [s]{/*}{*/},
 morestring=[b]", 
 sensitive = true,
 morekeywords = {abstract,  event,  new,  struct,
   as,  explicit,  null,  switch,
   base,  extern,  object,  this,
   bool,  false,  operator,  throw,
   break,  finally,  out,  true,
   byte,  fixed,  override,  try,
   case,  float,  params,  typeof,
   catch,  for,  private,  uint,
   char,  foreach,  protected,  ulong,
   checked,  goto,  public,  unchecked,
   class,  if,  readonly,  unsafe,
   const,  implicit,  ref,  ushort,
   continue,  in,  return,  using,
   decimal,  int,  sbyte,  virtual,
   default,  interface,  sealed,  volatile,
   delegate,  internal,  short,  void,
   do,  is,  sizeof,  while,
   double,  lock,  stackalloc,   
   else,  long,  static,   
   enum,  namespace,  string}
}

%\def\thesubsubsection{\thesubsection(\alph{subsubsection})}
\def\thesection{\Roman{section}}
\def\thesubsubsection{(\alph{subsubsection})}

\begin{document}

\begin{flushright}
{ECE 4570}\\{E04}\\{Ben Andrews (bandrews@vt.edu)}\\{Alpha Chen (alchen@vt.edu)}\\{ECE-Blacksburg}\end{flushright}

\section{Report for the In-class Laboratory Session}

We couldn't get Ethereal to get a trace in time to turn this in.

\newpage
\section{Report for the At-home Assignment}

\subsection{}

See Appendix \ref{place-order-code}

\subsection{}

Since the pizza orders are written to a file or executed, there are several other functions that could be added to extend the utility of the PDA ordering system. A function to order drinks or get them refilled could be useful. Being able to pay via the PDA could also be an added function. Last, a function for setting the table location could be used to make serving the finished orders simpler.

\subsection{}

Web services use open standards and protocols, and thus provide greater interoperability between different platforms. They also work through HTTP, which is a common protocol and thus unlikely to be blocked or need configuration.

However, it is not as efficient as RPC, as data is not encoded and parsing not optimized. RPC is also easier to use, as it doesn't require HTTP to run.

\subsection{}

Web services can be used for a variety of applications. Web frameworks can present a WDSL public interface for any web application created with such a framework. With the variety of web applications available today, two other application areas include uploading data from mobile devices and interfacing with other web applications.

\newpage
\section{Conclusion}

This lab showed how to use web services (SOAP) from both the client and server side. We first programmed a small application to send pizza orders to a server. This showed one application of the technology, where a mobile device could interact with an application to make life easier. The at-home assignment required us to write the back-end for the server. This was not complicated, and showed how a simple SOAP application is programmed and used.

\appendix

\newpage
\section{placeOrder}
\label{place-order-code}

\lstinputlisting[language=CSharp]{PizzaService1/PizzaService1/Service1.asmx.cs}

\end{document}